Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-11-03 RR_manuscript/Draft_RR.Rmd
fixed figure 3

```{r plot-meta1, echo = FALSE, fig.cap="(ref:plot-meta1)", out.width="100%"}
knitr::include_graphics(here::here("./figs/meta_plot1_raw.png"), error = FALSE)
```

>>>>

```{r plot-meta1, echo = FALSE, fig.cap="(ref:plot-meta1)", out.width="100%"}
knitr::include_graphics(here::here("./figs/meta_plot1_shrinkage.png"), error = FALSE)
```
